Pteropod biomarker analysis

### 2018-04-02 biomark.Rmd
ggally added with smooths on biomark

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)
library(plotly)

@@

>>>>

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)
library(plotly)
library(GGally)

@@

Pairs plot showing only LPX, SOD, ORAC/LPX with omega, O2, T:
```{r, fig.height = 8, fig.width = 8}
dat2 <- ptedat %>% 
  inner_join(envdat, by = 'CTD') %>% 
  select(one_of(c('LPX', 'SOD', 'ORACvLPX', 'Ara', 'O2', 'Temp')))

# Function to return points and geom_smooth
my_fn <- function(data, mapping, method="loess", ...){
      p <- ggplot(data = data, mapping = mapping) + 
      geom_point() + 
      geom_smooth(method=method, ...)
      p
    }

# Default loess curve    
ggpairs(dat2, lower = list(continuous = my_fn))
```
